Generalized spaces for constructive algebra

### 2020-04-09 paper-herrsching2019/main.tex
typo

\textbf{Definition.} A \emph{topological space} consists of a set~$X$ of points
together with a set~$\OOO(X) \subseteq \P(X)$ of point sets which are deemed
\emph{open} such that (arbitrary, set-indexed) unions and finite intersections
of open sets are open.
\end{quote}

>>>>

\textbf{Definition.} A \emph{topological space} consists of a set~$X$ of points
together with a set~$\OOO(X) \subseteq P(X)$ of point sets which are deemed
\emph{open} such that (arbitrary, set-indexed) unions and finite intersections
of open sets are open.
\end{quote}
